A Detection of the Environmental Dependence of the Sizes and Stellar Haloes of Massive Central Galaxies

### 2017-07-26 draft/paper2_v3.tex
Edit introduction

% Version 0; preprint format; Outline of paper II by Song Huang
% Version 1; preprint format; Edited by Jenny Greene
% Version 2; preprint format; Edited by Song Huang

@@

\def\etal{{\ et al.~}}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}
\def\redm{\texttt{redMaPPer}}
\def\cmodel{\texttt{cModel}}
% Samples
\def\rbcg{\texttt{cenHighMh}}
\def\nbcg{\texttt{cenLowMh}}
\def\redbcg{{$\lambda \ge 30$}}
\def\nonbcg{{$\lambda < 20$}}
% Mass related 
\def\mstar{{$M_{\star}$}}
\def\mhalo{{$M_{\mathrm{200b}}$}}
\def\logms{{$\log (M_{\star}/M_{\odot})$}}
\def\logmh{{$\log (M_{\mathrm{200b}}/M_{\odot})$}}

@@

\title[Structure and Environment of Massive Galaxies]{
       A Detection of the Environmental Dependence of the Stellar Profiles and haloes
       of Massive Central Galaxies}

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        Alexie Leauthaud,$^{2,1}$
        Jenny Greene,$^{4}$
        Kevin Bundy,$^{3,1}$
        \newauthor
        Yen-Ting Lin,$^{5}$
        Masayuki Tanaka,$^{6}$
        Rachel Mandelbaum,$^{7}$
        Satoshi Miyazaki,$^{5,8}$
        \newauthor
        Yutaka Komiyama$^{5,8}$
        \\
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
              Tokyo 181--8588, Japan\\
        $^{6}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{7}$McWilliams Center for Cosmology, Department of Physics, 
              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
        $^{8}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
              Tokyo, 181--8588, Japan
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

@@

    One of the most intriguing observations of high-redshift galaxies from the last 
    decade has been the dramatic structural transformation in massive quiescent 
    galaxies \citep[e.g.][]{Trujillo2006, vanDokkum2008, Cimatti2008, Damjanov2009, 
    vanderWel2011, Szomoru2012, Patel2013} from $z \approx 2$ to the present. 
    These observations suggest that the progenitors of $z{\sim} 0$ massive early-type 
    galaxies (ETGs) need to increase their effective radius ($R_{\rm e}$) by factor 
    of 2--4 in the last 10 Gyrs (e.g. \citealt{Newman2012, vdWel2014}).
    They have led to a ``two-phase'' scenario for the formation of massive ETGs 
    (e.g. \citealt{Oser2010, Oser2012}),
    in which galaxies form a compact central region through highly dissipative 
    processes (e.g. gas-rich merger or cold gas-accretion; 
    \citealt{Hopkins2008, Dekel2009}) and then assemble their extended stellar 
    haloes via dry mergers 
    \citep[e.g,][]{Naab2006, Khochfar2006, Oser2010, Oser2012}, which allows for 
    significant growth at late times. 
    Meanwhile, progenitor bias, which proposes that larger ETGs were quenched more 
    recently, could also contribute to the apparent size growth, although its 
    important is under argument (e.g. \citealt{Newman2012, Carollo2013, 
    Poggianti2013, Belli2015, Keating2015, Fagioli2016}).

    Several previous works have tested the two-phase formation scenario 
    observationally using galaxies at low redshift, looking at their surface 
    brightness of mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
    Oh2017}, optical color gradients (e.g. \citealt{LaBarbera2010, LaBarbera2012}), 
    and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
    Greene2015, Barbosa2016}. 
    These observations are generally consistent with the two-phase scenario, 
    but this picture still face many challenges.
    One of the most outstanding issues is the extent to which, at fixed stellar mass, 
    the accreted fraction depends on the surrounding dark matter halo mass.

    According to this two-phase formation scenario, the late time growth of massive 
    ETGs is intrinsically tied to the growth of their host dark matter haloes 
    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Massive ETGs that live at the center of more massive haloes should experience 
    different assembly and should be subject to higher merger rate compared to 
    ETGs with similar \mstar{} that live in less massive dark matter haloes. 
    A natural prediction of this picture is therefore that the structures of 
    massive ETGs should depend on their ``environment''\footnote{There are 
    different definitions of ``environment'' in the literature.  
    In this work, we use ``environment'' and halo mass interchangeably.}.
    For instance, models based on two-phase scenario predict that the well-know 
    stellar mass--effective radius relation for ETGs (\mstar{}--$R_{\rm e}$ relation; 
    e.g., \citealt{Shen2003, Guo2009}) should show environmental dependence: the 
    $R_{\rm e}$ of massive ETGs in more massive haloes should be larger than those 
    in less massive haloes at fixed \mstar{} 
    (e.g. \citealt{Shankar2013, Shankar2014}).
    Yet, solid evidence of this effect at low redshift is still missing 
    (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}).

@@

    To seriously test the environmental dependence of structure in massive ETGs 
    requires highly sensitive observations extending beyond the inner region of these 
    galaxies to truly probe the material accreted at late times. 
    This is very challenging observation as the surface brightness drops rapidly 
    with radius in massive ETGs.

    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that the deep, 
    multi-band images from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
    HSC-DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
    Miyazaki in~prep.) allows us to extract robust surface stellar
    mass density (\mden{}) profiles for {\it individual} massive galaxies 
    at $0.3 < z < 0.5$ out to 100 kpc. 
    In Paper I, we exploited this sensitivity to show that the \mden{} profiles 
    and the shapes of the stellar haloes of massive ETGs has a clear \mstar{} 
    dependence. 
    And the fraction of accreted stars residing in the extended envelope increases
    with the total \mstar{} of the galaxy.

    In this paper, we explore how the extended stellar halo in massive central galaxies
    depends on dark matter halo mass with the help of HSC images of a large sample 
    of massive ETGs and the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
    \citealt{Rozo2015b}; please see \S \ref{sec:data} for details)

    This paper is organized as follows. 
    \S \ref{sec:data} briefly introduce the sample selection and data reduction 
    processes.  
    Please refer to \citet{hscMassiveI} for more technical details.
    Our main results are presented in \S \ref{sec:result} and discussed in 
    \S \ref{sec:discussion}. 
    \S \ref{sec:summary} presents our summary and conclusions.

    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
    extinction using calibrations from \citet{Schlafly11}.
    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
    and ${\Omega}_{\rm \Lambda}=0.7$.
    Stellar mass is denoted \mstar{} and has been derived using a Chabrier Initial Mass 
    Function (IMF; \citealt{Chabrier2003}).

    Halo mass is defined as $M_{\rm 200b}$ as 
    $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
    is the radius at which the mean interior density is equal to 200 times
    the mean matter density ($\bar{\rho}$).

    As in \citet{hscMassiveI}, we do not try to separate any potential ``intra-cluster''
    component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}) from 
    massive galaxies in our sample for both technical and scientific reasons.  
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \caption{
          The environmental dependence of the stellar mass profiles of massive central 
          galaxies. 
          The left panel corresponds to samples matched by ``total'' stellar mass 
          (\mtot{}). 
          The right panel corresponds to samples matched by ``core-mass'' (\minn{}). 
          Orange and red lines correspond to central galaxies living in haloes with 
          \logmh{} $\geq 14.2$. 
          Black and grey correspond to central galaxies living in haloes with 
          \logmh{} $\leq 14.0$. 
          Thin lines show the profiles of individual galaxies while thick lines show 
          the median profile. 
          The uncertainty on the median profile is given by the shaded region and is 
          computed via bootstrap resampling. 
          The brown line in the bottom panels show the relative difference between 
          two median profiles 
          ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
          \log(\mu_{\star, \mathrm{cenLowMh}})$). 
          Errors on the difference between the two profiles is computed via bootstrap 
          too. 
          The grey shaded regions show a Monte Carlo test to asses how likely is it to 
          obtain $\Delta$ from random sub-samples of the data. 
          To compute the grey shaded regions, we first mix the two samples 
          (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
          population and compute $\Delta$ in the same fashion as for our fiducial signal. 
          We repeat this process 5000 times.  
          The dark-grey shaded region (light-grey shaded region) shows the 1-$\sigma$ 
          (3-$\sigma$) fluctuations in $\Delta$ from these 5000 draws.
          }
      \label{fig:prof_1} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    The sample selection and data reduction processes are described in detail in 
    Paper I. 
    Here we include a short summary for completeness.

    This work makes use of the imaging data from the internal data release 
    \texttt{S15B}, which is very similar to the Public Data Release 1 
    (\citealt{HSC-DR1} and covers ${\sim} 110$ deg$^2$ in all five-band ($grizy$) to 
    the required depth. 
    These images are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC (\citealt{HSC-PIPE}).
    The pixel scale of the reduced image is $0.168$\asec{}.
    We use the $i$-band image for extracting surface brightness profiles.    
    The HSC $i$-band image is typically 3--4 mag deeper than the SDSS one in surface 
    brightness limit and has superb seeing condition (mean FWHM$=0.6$\asec{}).

    In Paper~I, we select large sample of massive galaxies with either spectroscopic 
    redshift or reliable ``red-sequence'' photometric redshift (\citealt{Rykoff2014}) 
    at $0.3<z<0.5$. 
    Within this redshift range, we have large enough volume to achieve reasonable 
    statistics at very high \mstar{} end, can spatially resolve the inner $\sim 5$ 
    kpc of massive galaxies ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at 
    $z=0.3$ and 0.5), and can safely ignore any structural evolution. 
    We derive $i$-band surface brightness profiles out to 100 kpc after carefully 
    masking out any surrounding contaminations and correcting the background 
    subtraction. 
    We use the broadband spectral energy distributions (SED) fitting code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas13}) to measure the average \m2l{} and $k$--correction of 
    these galaxies using five-band forced \cmodel{} magnitudes from \texttt{hscPipe}.
    \citet{Chabrier2003} IMF, Flexible Stellar Population 
    Synthesis\footnote{http://scholar.harvard.edu/cconroy/sps-models}
    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}) model, 
    \citet{Calzetti2000} extinction law, simple delayed-$\tau$ model for star 
    formation history (SFH) are assumed here. 
    Using these information, we obtain reliable \mden{} profiles of these 
    galaxies out to $> 100$ kpc and \mstar{} integrated to different physical 
    radius using elliptical apertures.

    As explained in Paper I, here we focus on \mstar{} within

@@

        \item a 10 kpc radii (hereafter noted \minn{}) as proxy of the 
            \textit{in situ} stellar component. 
            This is motivated by recent observations and simulations 
            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}).

        \item a 100 kpc radii (hereafter noted \mtot{}), which is shown to recover 
            more \mstar{} than the ones based on \cmodel{} photometry, as proxy of the 
            total \mstar{} of the galaxy.

   \end{itemize}

   Although these radius are empirically selected, they help recover the 
   \mstar{}-dependence of the fraction of accreted stars, and reveal the diversity of 
   stellar envelopes among massive galaxies. 
   In Figure \ref{fig:m100_m10_color}, we demonstrate such diversity by showing 
   a random subsample of massive galaxies with very similar \minn{} that have large 
   range of \mtot{}. 
   We will use these two apertures\mstar{} to guide the comparisons of massive galaxies 
   from different environments.

@@

    In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
    In Paper~I, we demonstrate that the \mstar{} completeness above this threshold is 
    good over the full redshift range using comparisons with stellar mass functions 
    from more complete samples.

    We also wish to focus on massive galaxies that live at the centers of their own 
    dark matter haloes-- so-called ``central'' galaxies.  
    They are uniquely important to the study of galaxy-halo connection and are known 
    to follow stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
    Behroozi2013, Kravtsov2014, Tinker2017}) at high-\mstar{} end with small scatter.
    We utilize the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalog 
    to identify central galaxies.

    Firstly, we select 68 massive central galaxies from the \redm{} clusters 
    with $\lambda \geq 30$, $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$>11.5$ 
    at $0.3 < z < 0.5$ (63/69 have \logmtot{}$>11.6$). 
    This $\lambda$ limit is chosen to mitigate incompleteness of low richness clusters
    at the high end of our redshift window, and the $P_{\mathrm{Cen}}$ limit is 
    selected to exclude low probability candidate of central galaxy. 
    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these 
    galaxies are the brightest cluster galaxies (BCGs) of clusters with 
    \mhalo{}$>10^{14.2}$~\msun{}.
    This calibration is consistent with other works (e.g. \citealt{Saro2015, Farahi2016, 
    Melchior2016, Murata2017}). 
    The median richness of the sample is $\lambda \approx 41$ 
    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 
    only 44 central galaxies in clusters with $\lambda>50$ 
    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
    We will refer to this sample of \textbf{central galaxies in more massive haloes} as 
    the \rbcg{} sample.

>>>>

% Version 0; preprint format; Outline of paper II by Song Huang
% Version 1; preprint format; Edited by Jenny Greene
% Version 2; preprint format; Edited by Song Huang
% Version 3; preprint format; Edited by Alexie Leauthaud

@@

\def\etal{{\ et al.~}}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}
\def\redm{\texttt{redMaPPer}}
\def\cmodel{\texttt{cModel}}
% Samples
\def\rbcg{\texttt{cenHighMh}}
\def\nbcg{\texttt{cenLowMh}}
\def\redbcg{{$\lambda \ge 30$}}
\def\nonbcg{{$\lambda < 20$}}
% Mass related 
\def\mstar{{$M_{\star}$}}
\def\mhalo{{$M_{\mathrm{200b}}$}}
\def\logms{{$\log (M_{\star}/M_{\odot})$}}
\def\logmh{{$\log (M_{\mathrm{200b}}/M_{\odot})$}}
\def\logmhalo{{$\log (M_{\mathrm{200b}}/M_{\odot})$}}

@@

%\title[Structure and Environment of Massive Galaxies]{
%       A Detection of the Environmental Dependence of the Stelllar and haloes
%       of Massive Central Galaxies}

\title[Structure and Environment of Massive Galaxies]{
       A Detection of the Environmental Dependence of the Sizes and Stellar Haloes
       of Massive Central Galaxies}

\author[S. Huang et al.]{
        Song Huang$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)},
        Alexie Leauthaud$^{1}$,
        Jenny Greene$^{4}$,
        Kevin Bundy$^{3}$,
        \newauthor
        Yen-Ting Lin$^{5}$,
        Masayuki Tanaka$^{6}$,
        Rachel Mandelbaum$^{7}$,
        Satoshi Miyazaki$^{5,8}$,
        \newauthor
        Yutaka Komiyama$^{5,8}$
        \\
        $^{1}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{2}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\              
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
              Tokyo 181--8588, Japan\\
        $^{6}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{7}$McWilliams Center for Cosmology, Department of Physics, 
              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
        $^{8}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
              Tokyo, 181--8588, Japan
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

@@

    A key discovery in the last 
    decade has been the dramatic structural transformation of massive quiescent 
    galaxies \citep[e.g.][]{Trujillo2006, vanDokkum2008, Cimatti2008, Damjanov2009, 
    vanderWel2011, Szomoru2012, Patel2013} from $z \approx 2$ to the present day. 
    These observations suggest that the progenitors of $z{\sim} 0$ massive early-type 
    galaxies (ETGs) need to increase their effective radii ($R_{\rm e}$) by a factor 
    of 2--4 over a time span of 10 Gyrs (e.g. \citealt{Newman2012, vdWel2014}). 
    This observational result spurred the development of the ``two-phase'' formation
    scenario for massive ETGs (e.g. \citealt{Oser2010, Oser2012}),
    in which galaxies form a compact central region at $z\sim 2$ through highly 
    dissipative processes (e.g. gas-rich merger or cold gas-accretion;
    \citealt{Hopkins2008, Dekel2009}). 
    They subsequently assemble extended stellar haloes via dry mergers 
    \citep[e.g,][]{Naab2006, Khochfar2006, Oser2010, Oser2012} which can cause 
    significant size growth at late times. 
    An alternative explanation for size growth, progenitor bias, hypothesizes that 
    larger ETGs were quenched more recently, but this explanation is still under 
    active debate (e.g. \citealt{Newman2012, Carollo2013, Poggianti2013, Belli2015,
    Keating2015, Fagioli2016}).

    There have been multiple observational attempts to test the two-phase 
    formation scenario using galaxies at low redshift, by investigating surface 
    brightness or mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
    Oh2017}, optical color gradients (e.g. \citealt{LaBarbera2010, LaBarbera2012}), 
    and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
    Greene2015, Barbosa2016}. 
    These observations are generally consistent with the two-phase scenario, 
    but this picture still face many challenges.
    One of the most outstanding issues is the question of whether or not the 
    fraction of accreted stellar mass displays a dependency on dark matter halos mass.

    According to the two-phase formation scenario, the late time growth of massive 
    ETGs is intrinsically tied to the growth of their host dark matter haloes 
    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Massive ETGs living at the centers of more massive haloes should be subject to 
    higher merger rate compared to ETGs with similar \mstar{} but living in less 
    massive dark matter haloes. 
    A natural prediction of this picture is therefore that the structures of 
    massive ETGs should depend on their ``environment''\footnote{There are 
    multiple definitions of ``environment'' in the literature.  
    In this work, we use ``environment'' and halo mass interchangeably.}.
    Theoretical models based on the two-phase formation scenario predict an 
    environmental dependence of the stellar mass--effective radius relation for 
    ETGs (\mstar{}--$R_{\rm e}$; 
    e.g., \citealt{Shen2003, Guo2009}): the sizes of massive ETGs in more massive 
    haloes should be larger than those in less massive haloes at fixed \mstar{} 
    (e.g. \citealt{Shankar2013, Shankar2014}). 
    Yet, solid evidence of this effect at low redshift is still missing 
    (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}).

@@

    Testing this prediction requires deep imaging of ETGs in order to probe the 
    accreted component (the stellar halo) which can extend to 100 kpc and 
    beyond \citep[eg.,][]{hscMassiveI}. 
    This is very challenging observation as the surface brightness profiles of 
    massive ETGs decline rapidly with typical values of $\mu > 26.0$ \sb{} in 
    $i$-band at 100 kpc and at $z\sim0.3$. 
    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that deep, 
    multi-band imaging from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
    HSC-DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
    Miyazaki in~prep.) allows us to extract robust surface stellar
    mass density (\mden{}) profiles for {\it individual} galaxies with 
    \logms{}$>11.4$ at $0.3 < z < 0.5$ and out to 100 kpc. 
    In Paper I, we characterized the stellar mass distributions and mass density 
    profiles of stellar haloes of massive ETGs, and showed that there is a large 
    intrinsic scatter in the \mden{} stellar halos of massive galaxies on 100 kpc 
    scales, and that the fraction of accreted stars residing in the stellar halos 
    increases as a function of \mstar{}. 
    In this follow-up paper, we now address a fundamental prediction of the 
    two-phase formation scenario and conclusively show that the extended stellar 
    halos of massive central galaxies depend on dark matter halo mass. 
    In other terms, we reveal the halo mass dependence of the mass-size relation 
    for massive ETGs.

%    with the help of HSC images of a large sample 
%    of massive ETGs and the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
%    \citealt{Rozo2015b}; please see \S \ref{sec:data} for details)

    This paper is organized as follows. 
    In \S \ref{sec:data} we briefly introduce the sample selection and the data 
    reduction processes.  
    Please refer to \citet{hscMassiveI} for more technical details.
    Our main results are presented in \S \ref{sec:result} and discussed in 
    \S \ref{sec:discussion}. Section
    \S \ref{sec:summary} presents our summary and conclusions.

    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
    extinction using calibrations from \citet{Schlafly11}.
    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
    and ${\Omega}_{\rm \Lambda}=0.7$.
    Stellar mass is denoted \mstar{} and has been derived using a Chabrier Initial Mass 
    Function (IMF; \citealt{Chabrier2003}). Halo mass is defined as $M_{\rm 200b}$ as 
    $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
    is the radius at which the mean interior density is equal to 200 times
    the mean matter density ($\bar{\rho}$). 
    As in \citet{hscMassiveI}, we do not attempt to decompose or distinguish any  
    potential ``intra-cluster'' 
    component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}).

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \caption{
          The environmental dependence of the stellar mass profiles of massive central 
          galaxies. 
          Left: halo mass dependence of galaxy profiles at fixed ``total'' stellar mass 
          (\mtot{}). 
          Right: halo mass dependence of galaxy profiles at fixed ``inner-mass'' 
          (\minn{}). Orange and red lines correspond to central galaxies living in 
          haloes with \logmh{} $\geq 14.2$. 
          Black and grey lines correspond to central galaxies living in haloes with 
          \logmh{} $\leq 14.0$. 
          Thin lines show the profiles of individual galaxies while thick lines show 
          the median profile. 
          The uncertainty on the median profile is given by the shaded region and is 
          computed via bootstrap resampling. 
          Brown lines in the bottom panels show the relative difference between  
          two median profiles 
          ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
          \log(\mu_{\star, \mathrm{cenLowMh}}$). 
          Errors on the difference between the two profiles are also computed 
          via bootstrap.
          The grey shaded regions show a Monte Carlo test to asses how likely is it to 
          obtain $\Delta$ from random sub-samples of the data. 
          To compute the grey shaded regions, we first mix the two samples 
          (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
          population and compute $\Delta$ in the same fashion as for our fiducial 
          signal. 
          We repeat this process 5000 times.  
          The dark-grey shaded region (light-grey shaded region) shows the 1-$\sigma$ 
          (3-$\sigma$) fluctuations in $\Delta$ from these 5000 draws.
          }
      \label{fig:prof_1} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    We refer the reader to Paper I for an in-depth description of the sample selection 
    and data reduction processes. 
    Here, we briefly summarize the main steps.

    We use imaging data from the HSC internal data release 
    \texttt{S15B}, which is very similar to the Public Data Release 1 
    (\citealt{HSC-DR1} and covers ${\sim} 110$ deg$^2$ in all five-band ($grizy$) to 
    the full depth in the Wide field. The data are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC (\citealt{HSC-PIPE}).
    The pixel scale of the reduced image is $0.168$\asec{}.
    We use $i$-band images for extracting surface brightness profiles. HSC $i$-band images are typically 3--4 mag deeper than SDSS (spell out here and reference ?????)  and have superb seeing conditions (mean $i$-band seeing has FWHM$=0.6$\asec{}).

    In Paper~I, we select a sample of xxxxx(give number) massive galaxies with spectroscopic 
    redshifts or reliable ``red-sequence'' photometric redshifts (\citealt{Rykoff2014}) 
    at $0.3<z<0.5$. Within this redshift range, we have a large enough volume (xxx give the number here) to sample the galaxy mass function above $M-*>11.6$, we can spatially resolve galaxies profiles to $\sim 5$ 
    kpc ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at 
    $z=0.3$ and 0.5), and we can safely ignore structural evolution over our redshift range (give time span in Gyr xxx).

    We derive $i$-band surface brightness profiles out to 100 kpc after carefully 
    masking out surrounding neighbors and accounting for the subtraction of the background light. We use the broadband spectral energy distributions (SED) fitting code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas13}) to measure \m2l{} ratios and $k$--corrections using five-band forced \cmodel{} magnitudes from \texttt{hscPipe}. We assume a Chabrier IMF \citep{Chabrier2003}, the Flexible Stellar Population 
    Synthesis models\footnote{http://scholar.harvard.edu/cconroy/sps-models}
    (FSPS; \texttt{v2.4}; \citealt{FSPS}, \citealt{Conroy2010}), a Calzetti extinction law \citep{Calzetti2000}, and a simple delayed-$\tau$ model for star 
    formation histories (SFH). Using HSC data, we can measure the mass profiles of massive galaxies to $\sim 100$ kpc and we integrate these profiles within isophotal elliptical apertures at different physical radii. As explained in Paper I, here focus on the two following metric masses:

@@

        \item stellar mass within 10 kpc (hereafter noted \minn{}) which we use as a proxy for the 
            \textit{in situ} stellar component. This is motivated both by recent observations and simulations 
            (e.g.~\citealt{vanDokkum2010}, \citealt{RodriguezGomez2016}). The value of 10 kpc that we quote here corresponds to the radius of the major axis of the isophotal ellipse (xxx check).
        \item stellar mass within 100 kpc (hereafter noted \mtot{}). We use \mtot{} as a proxy of the total stellar mass. In Paper I we showed that \mtot{} recovers more light compared to HSC \cmodel{} photometry with offsets that can be a large as 0.2 dex in magnitude.           
   \end{itemize}

   We use these two simple metric masses to explore the 
   \mstar{}-dependence of the fraction of accreted stars, and reveal to the diversity of 
   stellar envelopes among massive galaxies. In practice, we also have the full profiles for each galaxy and can also cast our results in terms of the full stellar mass profiles. However, in many cases we find it more useful to display figures using the more simple \minn{} and \mtot{} quantities. In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a function of \minn{} and \mtot{}. Figure \ref{fig:m100_m10_color} shows a random subsample of massive galaxies with very similar \minn{} that have large 
   range of \mtot{}. 
   We will use these two apertures masses to guide our comparisons of massive galaxies as a function of environments.

@@

    In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
    In Paper~I, we demonstrate that this sample is almost mass complete over our full redshift range. In addition to the mass cut above, we also limit our sample to galaxies that live at the centers of their own 
    dark matter haloes-- so-called ``central'' galaxies. We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalog to construct a central galaxy sample.

    %Central galaxies are important to the study of galaxy-halo connection and follow stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
    %Behroozi2013, Kravtsov2014, Tinker2017}) at high-\mstar{}.

    Firstly, we select 68 massive central galaxies from \redm{} clusters 
    with $\lambda \geq 30$, $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$>11.5$ 
    at $0.3 < z < 0.5$ (63/69 have \logmtot{}$>11.6$). 
    This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalog
    at the high end of our redshift window. The $P_{\mathrm{Cen}}$ limit is 
    selected to exclude low probability central galaxy candidates. 
    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these corresponds to central galaxies living in halos with \mhalo{}$>10^{14.2}$~\msun{}. This calibration is consistent with other works (e.g. \citealt{Saro2015, Farahi2016, 
    Melchior2016, Murata2017}). 
    The median richness of the sample is $\lambda \approx 41$ 
    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 
    only 44 central galaxies in clusters with $\lambda>50$ 
    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
    We will refer to this sample of \textbf{central galaxies in massive haloes} as 
    the \rbcg{} sample.

    Secondly, we build a complementary sample of central galaxies in lower-mass haloes
    by excluding all galaxies that are in any \redm{} cluster with $\lambda > 20$.
    We convert their $\lambda$ into $M_{\mathrm{200b}}$ using calibration by 
    \citet{Simet2016}. 
    Then we estimate the $R_{\mathrm{200b}}$ of each cluster using the method in 
    \citet{Diemer2015}. We further exclude all galaxies within a cylinder around each cluster, with a radius
    equal to $R_{\mathrm{200b}}$ and a length equal to twice the value of the photometric 
    redshift uncertainty of the cluster (typically around 0.015 to 0.025). This second sample will be dominated by central galaxies living in haloes with
    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}. There are  833 galaxies with  
\logmtot{}$> 11.6$ in this sample.

%    Initially, we select 3453 galaxies this way with \logmtot{}$> 11.2$ at 
%    $0.3 < z < 0.5$ \alexie{Why do we care about this?}. 
%    Among them, 1564 (833) have \logmtot{}$> 11.5$ (11.6).

    Satellite contamination should be relative low at the high-\mtot{} end
    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
    For instance, the model from \citet{Saito2016} predicts a $\sim 7$\% 
    fraction for galaxies with \logmtot{}$>11.6$ and \logmh$<11.4$ haloes.

    In Appendix~\ref{app:basic}, we show the distributions of redshift, \mtot{}, and 
    \minn{} for the \rbcg{} and \nbcg{} samples. 
    We also compare these two samples on the \mtot{} - rest-frame $g-r$ color plane. 
    Both of them follow the same ``red-sequence'' with only a handful of galaxies displaying bluer colors.

    We note that our method fails to extract 1-D profiles for $\sim10$\% of 
    \rbcg{} and \nbcg{} galaxies due on-going major mergers or projection effects (e.g.\ nearby foreground galaxy or bright stars). However, this small failure rate should not affect any of the results in this paper.
